---
title: "Homework 6"
author: "firstName lastName"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
---
  
```{r, echo = FALSE, message = FALSE, eval = FALSE}
### Set up you workspace with the necessary data and packages
list.of.packages <- c("remotes", "tidyverse", "lubridate", "kableExtra", "forcats", "stringr", "glue") ## Vector of required packages for the assignment
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[, "Package"])] ## Check to see if these packages are installed
if(length(new.packages))
  install.packages(new.packages) ## Install the packages that aren't installed
library(remotes)

install_github("lter/lterdatasampler", force = FALSE) ## Install a package that isn't on CRAN
```


REMINDERS:  
- Unless otherwise requested, be sure to set up your R Markdown document to display only the resulting tibbles and the code used to generate them (unless otherwise requested). No errors or messages should print.    
- Tibbles appearing in your knitted document should be presented using kableExtra.  
- Remember to add your name in the YAML header.  


```{r echo = FALSE, message = FALSE}
###### The data set #####
## The code below generates a mock telemetry dataset containing observations of five fish at 10 different receiver stations. A second tibble contains common and latin names of each tagged species.

library(lubridate)
library(tidyverse)
fishDat <- sample(seq(as.POSIXct('2020/01/01'), 
           as.POSIXct('2022/02/28'), 
           by="5 mins"), 
       1000) %>% 
  as_tibble() %>% 
  mutate(fish = sample(c("Fish1", "Fish2", "Fish3", "Fish4", "Fish5"), replace = TRUE, 1000),
         receiverNumber = sample(1001:1010, 1000, replace = TRUE)) %>% 
  rename(obsTime = value) %>% 
  arrange(obsTime)

speciesDat <- as_tibble(c("walleye", "brown trout", "lake trout", "lake sturgeon", "lake whitefish")) %>% 
  rename(commonName = value) %>% 
  mutate(fishID = rep(paste0("Fish", c(1:5))), 
         genus = c("Sander", "Salmo", "Salvelinus", "Acipenser", "Coregonus"), 
         species = c("vitreus", "trutta", "namaycush", "fulvescens", "clupeaformis"))
```

**Question 1**. Determine the number of observations per month for each fish "genus_species".  
```{r}
# Answer 1

```

**Question 2**. How many lake sturgeon detections were on Tuesdays? Your final tibble should be just 1 row (any number of columns).     
```{r}
# Answer 2

```

**Question 3**. Determine the minimum time between detections and species ID for fish3. Your final tibble should be just 1 row (any number of columns).    
```{r}
# Answer 3

```

**Question 4**. Write a pipeline that subsamples one observation out of the joined dataset then prints a single sentence that describes the observation using data contained in every variable. The result should be a single, grammatically correct sentence.      
```{r}
# Answer 4

```

**Question 5**. Reorder the factor levels of the fishDat tibble's fish variable to "fish1, fish2, fish3, fish4, fish5." Add a second function to verify the order. Only print the first 10 rows of the resulting tibble.   
```{r}
# Answer 5

```

**Question 6**. After completing the joining the data tibble, use a stringr function to filter the observations to species containing the word "lake" then add a new column containing only the numerical portion of the fish number. Only print the first 10 rows of the resulting tibble.   
```{r}
# Answer 6

```
