---
title: "Homework 3"
author: "firstName lastName"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
---
  
```{r, echo = FALSE, message = FALSE}
### Set up you workspace with the necessary data and packages
list.of.packages <- c("remotes", "tidyverse", "kableExtra", "palmerpenguins") ## Vector of required packages for the assignment
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[, "Package"])] ## Check to see if these packages are installed
if(length(new.packages))
  install.packages(new.packages) ## Install the packages that aren't installed
library(remotes)

install_github("lter/lterdatasampler", force = FALSE) ## Install a package that isn't on CRAN
```


**Question 1: Tidy up a data set**   
Question 1a. What are the three rules of tidy data?   
```{r}
# Answer 1a
# Rule 1:
# Rule 2:
# Rule 3:
```

Question 1b. The tibble below describes data collected at three times on lakes and nearby trees. What aspects of this data set make it "messy"?     
```{r}
# Answer 1b
library(tidyverse)
hw3.tib <- tibble(
  sampleID = 1:10,
  tree_May = rnorm(10, 5, 1),
  tree_July = rnorm(10, 6, 1),
  tree_Sept = rnorm(10, 7, 1),
  lake_May = rnorm(10, 9, 1),
  lake_July = rnorm(10, 6, 1),
  lake_Sept = rnorm(10, 7, 1)
)

## This dataset is messy because: 

```

Question 1c. Tidy up the hw3.tib tibble using TidyR functions. Suppress the package loading message in your knitted document.     
```{r, message = FALSE}
# Answer 1c

```

Question 1d. But wait, this tibble isn't great because two pieces of information are squashed together in one variable. Separate the lake/tree and month variable into two different variables.     
```{r}
# Answer 1d

```

Question 1e. The previous question generated a well-formatted tibble. However, for some modeling applications, it may be useful to separate the tree and lake observations into separate variables. Use TidyR to wrangle your data into a form that has columns for the sample ID, the month the measurement was taken, the tree measurement, and the lake measurement.  
```{r}
# Answer 1e

```

Question 1f. Finally, improve the presentation of your final tibble using the kableExtra package discussed in week 1 of the course.  
  - Consult the kableExtra vignette to generate a table that is not the full width of the page and that prints in the font Cambria.  
  - Make sure that you suppress the printing of the package loading message in your knitted R Markdown.  
  - Also note that kableExtra will only print your polished table in your knitted document.  
```{r, message = FALSE}
# Answer 1f

```


**Questions 2: Working with helper functions**  
The select() function from the dplyr package (part of the Tidyverse) provides a way to subset columns. We'll discuss select() next week, but it is a useful tool for trying out various helper functions so we'll start working with it here.   

Question 2a. Use select() to subset the knz_bison dataset from the lterdatasampler package to contain only columns that end in "e"
```{r}
# Answer 2a

```

Question 2b. Use select() to produce a tibble containing only columns that contain the world "animal" in their name.  
```{r}
# Answer 2b

```

Question 2c. Combine the three date columns into a new column with the aid of a helper function.    
```{r}
# Answer 2c

```


**Question 3: Dealing with missing data**  
Question 3a.  There are several ways to deal with missing data using TidyR. Let's explore a few using the penguins() data set of the PalmerPenguins data package. First, use the table() function to determine how many male and female penguins are in the palmerpenguins::penguins data set. 
```{r}
# Answer 3a

```

Question 3b. Calculate the average bill length in the full data set. Be sure a numerical value is given.   
```{r}
# Answer 3b

```

Question 3c. Calculate the average bill length after using a TidyR function to get rid of the individuals with sex recorded as NA.     
```{r}
# Answer 3c

```

Question 3d. Use a TidyR function to fill in the missing sex values with the preceding sex value. View more of the resulting tibble using the "print()" function to ensure your solution is working correctly. Recalculate the number of male and females in this new data set, like you did in question 3a.    
```{r}
# Answer 3d

```

